Correlation between different emission channels from an atom inside a leaky driven cavity

### 2019-12-02 newpaper.tex
Add files via upload

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.5]{million1.pdf}
\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

@@

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{ccorr1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale = 0.5]{cnocorr1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma = \kappa =$ 1.0, $g =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
\end{center}
\end{figure}
\end{center}

The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.

>>>>

\begin{center}
\begin{figure}[t!]
\begin{center}
\includegraphics[scale = 0.5]{million1.pdf}
\caption{\small{Calculation of correlation using a time interval, tf = 500, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
\end{center}  
\end{figure}
\end{center}

@@

%\begin{center}
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[scale = 0.7]{lastgraph.pdf}
%\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = \kappa =$ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}  \label{errorzz}
%\end{center}
%\end{figure}
%\end{center}

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.7]{lastgraph.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500. (a) We consider $\kappa = $0.1 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.
